### 2019-10-03 paper/paper.tex
A bit more WIP

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{enumerate}
\usepackage{times}
\usepackage{color}
\usepackage{parskip}
\usepackage{afterpage}
\usepackage{setspace}
\usepackage[modulo]{lineno}
%\usepackage{xltxtra}
%\usepackage{xunicode}
\usepackage{gensymb}

@@

@@

%\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

@@

\cite{Karbowski2004} developed what remains, to the best of our knowledge, the
only dynamical model of cortical arealization capable of generating
predictions about the influence of signalling molecules on the size, shape,
and topological organization of emergent cortical fields. This model describes
competition between thalamocortical projections for territory along a
one-dimensional string of cortical cells, e.g., along an anterior-posterior
axis. The equations of the model define how the density of connections, $c$,
and the density of axon branches, $a$, interact at time $t$ at each cortical
location $x$, for $N$ thalamocortical projections indexed by $i$. The Voronoi
tesselation used to describe barrel patterning is a two-dimensional structure,
hence we first extended the original model for simulation on a two-dimensional
cortical sheet, and describe it here as such (i.e., substituting $x$ for the
two-dimensional position vector $\mb{x}$ and substituting terms of the form
$\frac{d}{dx}$ for the two-dimensional spatial operator $\nabla$).

@@

The first term on the right describes the spatial gradient (indicated by
$\nabla\vcdot$) of a quantity referred to in models of heat diffusion as the
`flux' (the term enclosed by parentheses). The central idea in heat diffusion
models is that the change in temperature (over time) at a given location is
proportional to the gradient in the temperature (over space) at that
location. Substituting heat for the branching density, axons from a given
thalamic projection are thus assumed to branch laterally across the cortical
sheet at a rate given by the diffusion constant $D$. Lateral branching is
augmented by a measure of the local alignment between the branching density
and the gradient in the concentration of each of $M$ distinct molecular
signals, $\rho(\mb{x})$. The influence of a given signal (indexed by $j$) on a
given thalamic projection (indexed by $i$), is determined by the parameter
$\gamma_{i,j}$. Interactions for which this value is positive encourage axon
branching in the direction in which the concentration of the signal is
increasing, whereas negative interactions encourage branching in the opposite
direction. Hence the axons of a given thalamic projection are assumed to
branch towards either higher or lower concentrations of each signalling
molecule.

@@

\subsection*{}

\subsection*{Relative interaction strengths}

@@

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{enumerate}
\usepackage{times}
\usepackage[usenames]{color}
\usepackage{parskip}
\usepackage{afterpage}
\usepackage{setspace}
\usepackage[modulo]{lineno}
%\usepackage{xltxtra}
%\usepackage{xunicode}
\usepackage{gensymb}

@@

\usepackage{lmodern}

@@

% Blue for comments
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Code in sans serif
\newcommand{\code}[1]{\textsf{#1}}
% Divergence symbol (Del dot Del)
\newcommand{\dvrg}{\nabla\vcdot\nabla}
% Emphasis shortcut
\newcommand{\e}{\emph}
% Bold shortcut
\newcommand{\bol}{\textbf}
% Math bold
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

@@

\cite{Karbowski2004} developed what remains, to the best of our knowledge, the
only dynamical model of cortical arealization capable of generating
predictions about the influence of signalling molecules on the size, shape,
and topological organization of emergent cortical fields. This model describes
competition between thalamocortical projections for territory along a
one-dimensional string of cortical cells, e.g., along an anterior-posterior
axis. The equations of the model define how the density of connections, $c$,
and the density of axon branches, $a$, interact at time $t$ at each cortical
location $x$, for $N$ thalamocortical projections indexed by $i$. The Voronoi
tesselation used to describe barrel patterning is a two-dimensional structure,
hence we first extended the original model for simulation on a two-dimensional
cortical sheet, and describe it here as such (i.e., substituting $x$ with the
two-dimensional position vector $\mb{x}$ and substituting terms of the form
$\frac{d}{dx}$ with the two-dimensional spatial gradient operator $\nabla$).

@@

The first term on the right describes the spatial gradient (indicated by
$\nabla\vcdot$) of a quantity referred to in models of heat diffusion as the
`flux' (the term enclosed by parentheses). The central idea in heat diffusion
models is that the change in temperature (over time) at a given location is
proportional to the gradient in the temperature (over space) at that
location. Substituting the branching density for heat, axons from a given
thalamic projection are thus assumed to branch laterally across the cortical
sheet at a rate given by the diffusion constant $D$. Lateral branching is
augmented by a measure of the local alignment between the branching density
and the gradient in the concentration of each of $M$ distinct molecular
signals, $\rho(\mb{x})$. The influence of a given signal (indexed by $j$) on a
given thalamic projection (indexed by $i$), is determined by the parameter
$\gamma_{i,j}$. Interactions for which this value is positive encourage axon
branching in the direction in which the concentration of the signal is
increasing, whereas negative interactions encourage branching in the opposite
direction. Hence the axons of a given thalamic projection are assumed to
branch towards either higher or lower concentrations of each signalling
molecule.

@@

\cmnt{If we need to present the results of the 2-D system with $\chi=0$, then
  we'll do that first, showing a 2-D version of the simulation obtained by
  running \code{james0 configs/karb.json}}

We first verified that the system given by Eqns. \ref{eq:Karb2DExt_dc} \&
\ref{eq:Karb2DExt_da} described a two dimensional extension of the axon
branching model in \citet{Karbowski2004}. We showed that in the presence of
three guidance gradients varying only in one dimension (along the long axis of
an elliptical domain), five thalamocortical axon types, each interacting
uniquely with the three guidance gradients, would segregate into five separate
regions. We investigated a number of configurations of the guidance gradients,
varying their shape, $\rho(\mb{x})$, and number, $M$, and their effect on a
varying number of thalamocortical projections, $N$. In general, we were not
able to produce structure in the resulting patterns of the connections,
$c(\mb{x},t\rightarrow\infty)$, which was not present in the guidance
patterns.

Complex structure can indeed be observed in protein expression for some genes,
such as the molecules Bhlhb5 \citep{Joshi2008} and Lmo4
\citep{Cederquist2013,Greig2013}. These expression patterns can therefore
provide a theoretical mechanism for the guidance of axons into distinct
regions, shifting the explanation of how such structures are generated into
the realm of gene transcriptional interactions and mRNA diffusion/movement
(\cmnt{Fixme: find a ref on structure in gene transcription}). However,
complex, stable structure in gene expression is less commonly reported than
homogeneous or simply varying expression, such as Pax6, Emx2, Coup-TF1 which
display graded expression across the entire isocortex
(\cmnt{REFS}). Furthermore, the complex structure observed in the whisker
barrel field has not, to our knowledge, been linked to a complex set of gene
expression patterns matching the scale of the barrels. To investigate how the
whisker barrel structure might form in the presence of only two
coordinate-giving morphogen gradients, we turned our attention to the
competition for connections built into the model.

There exists an element of competition in the model system specified by
Eqns. \ref{eq:Karb2DExt_dc} \& \ref{eq:Karb2DExt_da}.

\subsection*{Basic results}

Formation of a grid of domains, with somatotopic ordering.

Fig of domains.

\subsection*{With surrounding large domains}

Maybe, put this in to remind myself that I did this. It looks nice.

\subsection*{Plucking experiments}

Include results of plucking a single whisker, a row of whiskers and a
column of whiskers.

\subsection*{Any parameter sweeps necessary to show behaviour is
  robust to changes in params}

Go here.

\subsection*{Manipulating Competition: Group competition stronger/weaker than inter-group competition}

Just an idea - have two separate epsilons.

\subsection*{Manipulating Guidance: Relative interaction strengths}

@@

\subsection*{Manipulating Guidance: Delayed onset in one axis}

Another idea; begin with only one guidance gradient, or one strong and
one very weak guidance gradient, and begin the development in this
form, so as to encourage the formation of rows. Subsequently, turn on
the second strong guidance signal.

\subsection*{Manipulating Guidance: Different guidance profiles}

Linear, circ linear, exponential, etc.
